The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-10 paper/ms.tex
fig 1.eps
Width plot in the paper
Fig 8 improved
Lambda dertmined

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

\usepackage{graphics}
\usepackage[dvips]{epsfig}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{f1_1.eps}
  \includegraphics[width=0.45\textwidth]{f1_2.eps}
\end{center}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

The central result of this paper is summarized in Figure
\ref{fig:differentvelocities}. It shows the evident
impact of rotation on the morphology of the emergent \ly line. Both
panels focus on the results for $\tau_{H}=10^{7}$, showing that the
influence of rotation is present both when the photons are either
homogeneously or centrally initialized over the gas volume.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{NewWidthVvsVmax.eps}
    \caption{Half-width for the non-dusty models as a function of
      rotational velocity $V_{\rm max}$. Continuous (dashed) lines
      correspond to central (homogeneous) source
      distributions. \label{fig:widthvsvelocity}} 
\end{figure}

\begin{figure}
    \includegraphics[width=0.45\textwidth]{f3.eps}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure}

@@

We parameterize the dependency of the linewidth as $W^2 =
W_{0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity witdth can be expressed as a
quadratic sum of the two relevant velocities in the problem. We find
that for $\lambda = x\pm y$ ($\lambda=x\pm y$) for the central
(homogeneous) sources.

In order to quantify the transition to a single peak we measure the
position for the peak maxima as a function of the rotational
velocity. Our results are presented in Figure
\ref{fig:maximumsvsvelocity} where it is clear that for central
sources there are always two peaks with fixed positions as the rotational
velocity changes. However, in the case of homogeneously emitted
sources the maxima position remain close to constant until some
velocity threshold the line becomes single peaked with $x_{\rm m}=0$
\kms. {\bf By inspection we find that in all cases the transition has
occurred when the rotational velocity is larger than the intrinsic
linewidth OR HALF WIDTH ONCE THE NUMBERS ARE FIXED?}.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{f4.eps}
\caption{Logarithm of the average number of scatterings as function of
  rotational velocity. Continuous (dashed) lines represent an
  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{f5_1.eps}
  \includegraphics[width=0.45\textwidth]{f5_2.eps}
  \includegraphics[width=0.45\textwidth]{f5_3.eps}
  \includegraphics[width=0.45\textwidth]{f5_4.eps}    
\end{center}
    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
      show the homogeneous (central) source distribution. Left
      corresponds to the static case and right
      $V_{\rm max}=300\kms$. The color scale is logarithmic on the
      number of photons with given values of $N_{\rm scatt}$ and
      $x$. \label{fig:Nscatt2D}}   
\end{figure*}

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{f6.eps}
  \caption{Escape fraction as a function of rotational velocity. All
    these models have $\tau_{a}=1$. The continuous (dashed) lines
    correspond to central (homogeneous) models.
    \label{fig:efvsv}}
\end{figure}

\begin{figure}
  \includegraphics[width=0.45\textwidth]{f7.eps}
  \caption{Escape fraction as a function of the
    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
    the infinite slab is shown as a continuous line. Different dashed
    lines correspond to different rotational velocities.
    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
    \label{fig:efvsNeufeld}}   
\end{figure}

In the case of dusty clouds, all changes in the average number
of scatterings presented in the previous subsection have a direct
bearing on the escape fraction. From the results we have just obtained
we can predict that for central source distributions the escape
fraction will barely change, while larger effects should be expecte
for homogeneously distributed sources.

@@

\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.3]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. {\bf Si el observador esta en j, entonces las
    dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
    hacer las dos circulos pequenos punteados. Por otro lado, como se
    habian definido las velocidades, el eje de rotacion es el eje k}
    \label{fig:OCspheres}} 
\end{figure}

\begin{figure}
  \includegraphics[scale=0.35]{f9.eps}
  \caption{$\mu$ histogram showing the orientation effects for the different
  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
    \label{fig:muhisto}} 
\end{figure}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.3]{f10.eps}
\end{center}
\caption{\ly profiles for the off-centered emission. Dashed/solid
  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
   \label{fig:OC_profiles}} 
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.3]{f11.eps}
\caption{Triple peaked profiles for three different off-center positions
  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
  line) and for different rotational velocities.  
   \label{fig:3p_profiles}} 
\end{figure*}

@@

{\bf Figure \ref{fig:3p_res} show that even with a low resolution a three-peak profile 
would be observed, this is important for observational porpoises due to the finite 
spectral resolution. Seguro? Que es baja resolucion y que es alta
resolucion en este contexto?}

\begin{figure}
\begin{center}
\includegraphics[scale=0.3]{f12.eps}
\end{center}
\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
   \label{fig:3p_res}} 
\end{figure}

>>>>

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{f1.eps}
\end{center}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

The central result of this paper is summarized in Figure
\ref{fig:differentvelocities}. It shows the evident
impact of rotation on the morphology of the emergent \ly line.
The panel focus on the results for all of our symmetric models
 $\tau_{H}=10^{6}, 10^{6}, 10^{5}$, showing that the
influence of rotation is present both when the photons are either
homogeneously or centrally initialized over the gas volume.

@@

\begin{figure*}
    \includegraphics[width=1.0\textwidth]{f2.eps}
    \caption{Half-width for the non-dusty models as a function of
      rotational velocity $V_{\rm max}$. Continuous (dashed) lines
      correspond to central (homogeneous) source
      distributions. \label{fig:widthvsvelocity}} 
\end{figure*}

\begin{figure}
    \includegraphics[scale=0.4]{f3.eps}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure}

@@

We parameterize the dependency of the linewidth as $W^2 =
W_{0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity witdth can be expressed as a
quadratic sum of the two relevant velocities in the problem. We find
that for $\lambda = 3.895$ ($\lambda= 1.982$) for the central
(homogeneous) sources.

In order to quantify the transition to a single peak we measure the
position for the peak maxima as a function of the rotational
velocity. Our results are presented in Figure
\ref{fig:maximumsvsvelocity} where it is clear that for central
sources there are always two peaks with fixed positions as the rotational
velocity changes. However, in the case of homogeneously emitted
sources the maxima position remain close to constant until some
velocity threshold the line becomes single peaked with $x_{\rm m}=0$
\kms. By inspection we find that in all cases the transition has
occurred when the rotational velocity is larger than half width .

@@

\begin{figure}
    \includegraphics[scale=0.4]{f4.eps}
\caption{Logarithm of the average number of scatterings as function of
  rotational velocity. Continuous (dashed) lines represent an
  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[scale=0.35]{f5_1.eps}
  \includegraphics[scale=0.35]{f5_2.eps}
  \includegraphics[scale=0.35]{f5_3.eps}
  \includegraphics[scale=0.35]{f5_4.eps}    
\end{center}
    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
      show the homogeneous (central) source distribution. Left
      corresponds to the static case and right
      $V_{\rm max}=300\kms$. The color scale is logarithmic on the
      number of photons with given values of $N_{\rm scatt}$ and
      $x$. \label{fig:Nscatt2D}}   
\end{figure*}

@@

\begin{figure}
  \includegraphics[scale=0.4]{f6.eps}
  \caption{Escape fraction as a function of rotational velocity. All
    these models have $\tau_{a}=1$. The continuous (dashed) lines
    correspond to central (homogeneous) models.
    \label{fig:efvsv}}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.4]{f7.eps}
  \caption{Escape fraction as a function of the
    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
    the infinite slab is shown as a continuous line. Different dashed
    lines correspond to different rotational velocities.
    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
    \label{fig:efvsNeufeld}}   
\end{figure}

In the case of dusty clouds, all changes in the average number
of scatterings presented in the previous subsection have a direct
bearing on the escape fraction. From the results we have just obtained
we can predict that for central source distributions the escape
fraction will barely change, while larger effects should be expected
for homogeneously distributed sources.

@@

\label{sec:off-center}
\begin{figure}
\begin{center}
  \includegraphics[scale=0.4]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. 
    \label{fig:OCspheres}}

\end{center}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.4]{f9.eps}
  \caption{$\mu$ histogram showing the orientation effects for the different
  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
    \label{fig:muhisto}} 
\end{figure}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.35]{f10.eps}
\end{center}
\caption{\ly profiles for the off-centered emission. Dashed/solid
  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
   \label{fig:OC_profiles}} 
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.4]{f11.eps}
\caption{Triple peaked profiles for three different off-center positions
  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
  line) and for different rotational velocities.  
   \label{fig:3p_profiles}} 
\end{figure*}

@@
